---
title: "Initial_Summary"
author: "Aditya"
date: "4/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(ggplot2)
reddit1900=read.csv("/Users/adityabhat/Downloads/Datasets/Reddit_Dataset.csv")
```

### Number of Unique Stories
```{r}
length(unique(reddit1900$id))
```

### % of Unique stories
```{r}

(length(unique(reddit1900$id))/nrow(reddit1900))*100

```


```{r}
#unique_visitors=as.data.frame(unique(reddit1900$active_users))
active_users=read.csv("/Users/adityabhat/Downloads/Datasets/Visitors.csv")
```
### Unique Visitors between Night and Day
```{r}
ggplot(active_users,aes(x=Date,y=Active_Users,group=TimeOfDay))+geom_line(aes(color=TimeOfDay))+geom_point(aes(color=TimeOfDay))+theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=7, angle=90))
```

### T-Test to check for signifance in the no of active users between day and night
```{r}
t.test(active_users$Active_Users~active_users$TimeOfDay)
```

### No of unique Visitors Between Weekend and Weekdays
```{r}
ggplot(active_users,aes(x=Date,y=Active_Users,group=TypeOfDay))+geom_line(aes(color=TypeOfDay))+geom_point(aes(color=TypeOfDay))+theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=7, angle=90))
```
### No of unique Visitors Between Weekend and Weekdays (Bar plot)
```{r}
ggplot(active_users,aes(x=Date,y=Active_Users))+geom_point()+facet_wrap(~TypeOfDay)+theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=7, angle=90))
```

```{r}
### code to get dataset of only unique rows
#reddit_unique=reddit1900[!duplicated(reddit1900[, c("id")]),]
reddit_unique=read.csv("/Users/adityabhat/Downloads/Datasets/Reddit_Unique.csv")
```
### Length of the articles ( Less than 500 words is short and greater than 500 words is Long)
```{r}
ggplot(reddit_unique,aes(x=DocLen))+geom_bar(fill="steelblue")+
   theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=7, angle=90))
  
```

### Type of News Organization
```{r}
ggplot(reddit_unique,aes(x=SourceType))+geom_bar(fill="steelblue")+
  theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=7, angle=90))
```

### Importance of Stories
```{r,warning=FALSE}
ggplot(reddit1900,aes(x=Repeated))+geom_bar(fill="steelblue")+
  theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=7))
```

### % of Stories with Social Media Postings
```{r}
sm=subset(reddit_unique,reddit_unique$Social_Media>0)
(nrow(sm)/nrow(reddit_unique))*100
```

### % of Stories with atleast 1 Video
```{r}
video_1=subset(reddit_unique,reddit_unique$Videos>0)
(nrow(video_1)/nrow(reddit_unique))*100
```

### % of Stories with multiple Videos
```{r}
video_1plus=subset(reddit_unique,reddit_unique$Videos>=2)
(nrow(video_1plus)/nrow(reddit_unique))*100
```

### % of Stories with atleast 1 image
```{r}
photo1=subset(reddit_unique,reddit_unique$Images>0)
(nrow(photo1)/nrow(reddit_unique))*100
```

### % of Stories with multiple images
```{r}
photo1plus=subset(reddit_unique,reddit_unique$Images>1)
(nrow(photo1plus)/nrow(reddit_unique))*100
```

### Main Topics of articles with Social Media embeddings

```{r}
summary(sm$Topic1,maxsum = 5)
```

### Main topics in general
```{r}
summary(reddit_unique$Topic1,maxsum = 5)
```

### Average number of pictures in articles
```{r}

mean(reddit_unique$Images,na.rm=T)
```

### Average length of video in articles (Seconds)
```{r}
mean(reddit_unique$Video_Len,na.rm=T)
```

### Average social media embeddings in articles
```{r}
mean(reddit_unique$Social_Media)
```

